\chapter{Tools}
Throughout the whole process the group has used many tools to solve different kinds of tasks. This chapter will explain which tools that have been used and why.

\section{Designing tools}
In order to do prototyping and come up with design suggestion different tools have been used.

\subsection{Draw.io}
Draw.io is a free online tool, which can be used to create flowcharts, process diagrams, org charts, UML, ER and network diagrams.\cite{drawio}

\subsection{Ionic Creator}
Ionic Creator is a drag and drop tool for making and designing mobile applications. It uses pre-built components to quickly build and link pages together.\cite{ic)

\section{Development tools}
During the development process many tools and framework have been used solve different kinds of challenges. 

\subsection{AngularJS}
AngularJS, commonly known as Angular is an open-source web application framework developed mainly by Google. Angular simplifies the process between testing and development by providing a framework which is based on the model-view-controller architecture.\\
\\
The way Angular works is that it interprets a HTML page which consists of custom HTMLtag attributes. Angular then uses those attributes to bind directives to different parts of the page to a model, which is represented by regular JavaScript. Angular is a powerful tool which many big corporations use for their website today. \cite{angularjs}\cite{angularjs2}

\subsection{Ionic Lab}
Ionic Lab is a tool which makes it easy to test ones' application directly in the browser, with live reloading. It supports application testing on multiple screen sizes and platform types.\cite{ionicl}

\subsection{Github}
For collaborating on the source code the group used GitHub. This allows the group to have version control over the codebase This means if something goes wrong, or if  there are conflicting commits, it is easy to roll back to a previous version of code. \\
\\
Github works, in a large extent, as a cloud based storage drive for our source code. Local backups will be made, as a precautionary measure.

\subsection{NodeJS} To install Cordova, Ionic and other dependencies, NodeJS is required. NodeJS has a package community, npm, which is the largest community of open source libraries in the world. Npm is used to get and install both Cordova and Ionic from the open source community.\cite{nodejs}

\section{Project management tools}
To mange the project at remain control over all the different files and documents that have been created during the project. A 

\subsection{Trello}
Trello is a free to use web-based project management application that is mainly used to manage tasks. In Trello, projects are represented as boards which contains cards that represent the tasks. The reason for picking Trello over other project management tools is that it is simple and easy to use, and has the necessary functionality that the group needs to manage different aspects of the project using Scrum.

\subsection{Google drive}
Google has a broad set of collaborating tools, which the group was using throughout the project. Google drive was used to store the documents, photos and other files that were shared within the group.\\
\\
Google docs was one of the collaboration tools provided by google drive. It is an interface that enables real time editing from multiple users at the same time. It was very useful when planning, writing status reports, and editing of the preliminary report.\\
\\
Google Sheets is another service provided by Google drive. Sheets was used to manage the groups time sheet, so every person in the group can write down how many hours they have been working on the project each day. 

\subsection{Google calendar}
The group created a calendar to keep track of our internal meetings as well as the meetings with Vitensenteret and our supervisor. This calendar contained information about when and where to meet, and what kind of meeting it was.

\subsection{LATEX}
LATEX is a document preparation system that uses markup tagging to stylize the written document. It is a good way to structure documents, have interactive bibliographies, and easily create tables of contents.

\subsection{Sharelatex}
Sharelatex is a real-time online collaboration tool for editing and storing LATEX documents. Sharelatex is going to be used to write the final report. This makes it easy to collaborate on the report, and gives the final result a professional, and neat look.\\
\\
In addition to being a collaborative report writing tool, Sharelatex allows stores all the documents in the cloud, for easy access at all times. It does have version control, so it is easy to roll back a previous version of the document, if necessary.